Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-11 paper.tex
Try to clarify the relationship between direct interaction, Nell, and constructionism.

Children construct knowledge from direct interactive
experience~\cite{Papert91}. As a result, (and like its predecessor Sugar), Nell
emphasizes creation and tangible interaction by using direct interaction; this
time, using a tablet computer to maintain the child's connection to their work
(Fig.~\ref{fig:xo3}).

>>>>

Children often learn from direct interactive experience. Consequently, Nell
intensifies our commitment to constructionism~\cite{Papert91} by further
emphasizing creation and tangible interaction using a tablet computer as a way
to maintain the child's connection to their work (Fig.~\ref{fig:xo3}).
